---
title: "HW 0"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Problem 1: Create a 3x3 identity matrix and set the column/row names to a, b, c.
```{r}
 x <- diag(3)
rownames(x) <- c("a", "b", "c")
colnames(x) <- c("a", "b", "c")
x
```

Problem 2: Write a for loop that multiplies each value in a vector by 10.
```{r}
x <- c(1,3,5,7,9,11,13,15,17,19,21) 

 for(i in seq(to=10))

     score <- x * i
score
```

Problem 3: Repeat the previous problem, but using the appropriate apply (i.e., one of sapply, lapply, tapply, etc.) function.
```{r}
x <- c(1,3,5,7,9,11,13,15,17,19,21)

mult <- function(x) {  
  (x * 10)}
result <- sapply(x, mult)
result
```

Problem 4: Find the sum of all odd numbers from a to b.
```{r}
a = 100
b = 1000

odds <- sum(sapply(a:b, function(x) ifelse(x%%2, x, 0)))
odds
```

Problem 5: Plot the equation y=x^3+10.
```{r}
x <- seq(from=0, to=100, by=0.5)
y = x^3

plot(x,y)
```

Problem 6: Write a function that computes the GC content of a DNA sequence.

```{r}
#Had some issues with this one and converting it to a percentage and the whole thing is u g l y but it gives the right output!

x <- "AGGGCATACTAAGATGTGGCCCTACTACTGAGTATGGCGAT"

char.x <- strsplit(x, "")[[1]]
char.x

length(char.x)
G <- lengths(regmatches(x, gregexpr("G", x)))
C <- lengths(regmatches(x, gregexpr("C", x)))
all <- length(char.x)
all

GC <- (G+C)/all
GC

percent(GC, digits = 2, format = )

```

Problem 7: Write a function that finds the complement to a DNA sequence.
```{r}

#"ATCTCGGCGCGCATCGCGTACGCTACTAGC"
#chartr("ATGC","TACG",s)
```
